Computational Luminance Constancy from Naturalistic Images

### 2018-10-21 Production/Production.tex
editing figures for production

\usepackage{lineno}
\linenumbers
\begin{document}

@@

\section{Introduction}
The perceived color of an object has important behavioral implications because color helps to identify objects and their surface properties \cite{Mollon89, Jacobs81}.
The computational challenge underlying object color perception is that the light reflected from an object depends not just on the object's surface reflectance, but also 
on object-extrinsic factors such as the scene illumination, the pose of the object, and the viewpoint of the observer in the scene (Fig.~\ref{fig:introSchematic}).
To compute a perceptual representation of object color that is correlated with the object's physical surface reflectance, the visual system must account for these object-extrinsic factors.
The ability of a visual system to compute a representation of object color that is stable against variation in object-extrinsic factors is called color constancy. 
A well-studied special case of color constancy is when the stimuli are restricted to be achromatic. 
This special case is called lightness constancy \cite{gilchrist2006seeing}. 
Although human lightness and color constancy are not perfect, they are often very good \cite{FosterColorConstancy, BrainardColorConstancy,adelson2000,kingdom2011lightness}.

@@

% Figure 1: Introduction
\begin{figure}
\centering
\begin{subfigure}{0.4 \textwidth}
	\centering
	\caption{}
        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure1/Figure1_a.png}
        \label{fig:introSchematic}
    \end{subfigure}
    \begin{subfigure}{0.55 \textwidth}   
        \caption{}    
        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure1/Figure1_b.pdf}
        \label{fig:introExampleFigure}
    \end{subfigure}
    \label{introFigure}
    \caption{{\bf Color and luminance constancy:} (a)  The light reflected from an object to the eye depends both on the surface reflectance of the object and on the scene illumination. 
The reflected light also depends on geometric factors, such as the object's shape, pose, and position. 
The human visual system accounts for variations in reflected light due to object-extrinsic factors and produces a percept of object color that is relatively stable across such variations. 
(b) Images of a sphere under a fixed illuminant.  
Down each column, the sphere's luminous reflectance factor (LRF) varies, but its relative reflectance spectrum (i.e. its spectral shape) is held fixed.
Across each row, the relative reflectance spectrum varies, but the LRF is held fixed.
We cast the problem of computational luminance constancy to be that of estimating the LRF of a target object from the image, across variation in other scene factors. 
Specifically, we study variation in target object relative surface reflectance, variation in illumination spectrum, and variation in the surface reflectance of the other objects in the scene.}
 \end{figure}

@@

In this paper, we use high-quality computer graphics to generate large datasets of naturalistic images where the surface reflectance corresponding to each image pixel is known. 
This approach allows us to investigate computational color constancy with naturalistic stimuli, while retaining the ability to control the properties of objects and illuminants. We tackle the specific problem of luminance constancy, a constitutive component of the more general color constancy problem (Fig.~\ref{fig:introExampleFigure}).

@@

\section*{Methods} \label{Methods}
% Figure 2
\begin{figure}
\centering
\begin{subfigure}[b]{0.22 \textwidth}
        \caption{Library }
        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure2/Figure2_a.pdf}
        \label{fig:baseSceneLibrary}
    \end{subfigure}
    ~
    \begin{subfigure}[b]{0.22 \textwidth}
        \caption{Mill}    
        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure2/Figure2_b.pdf}
        \label{fig:baseSceneMill}
    \end{subfigure}    
    ~
    \begin{subfigure}[b]{0.22 \textwidth}
        \caption{Table-Chairs}    
        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure2/Figure2_c.pdf}
        \label{fig:baseSceneTableChairs}
    \end{subfigure}
    \caption{{\bf Base scenes.} Each image shows a rendering of one base scene without additional inserted objects.  The reflectance spectra of the distinct surfaces and the spectral power distributions of the light sources in each scene have been assigned randomly from statistical models of naturally occurring spectra. The images have been scaled and tone mapped individually for illustrative purposes.}
\label{fig:baseScenes}. \end{figure}

@@

% Figure 3
\begin{figure}
\centering
    \begin{subfigure}[b]{0.14 \textwidth}
        \caption{Big-ball}
        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure3/Figure3_a.png}
        \label{fig:libraryWithBigBall}
    \end{subfigure}
     ~ 
    \begin{subfigure}[b]{0.14 \textwidth}
        \caption{Xylophone}
        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure3/Figure3_b.png}
        \label{fig:libraryWithXylophone}
    \end{subfigure}
     ~ 
    \begin{subfigure}[b]{0.14 \textwidth}
        \caption{Barrel}
        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure3/Figure3_c.png}
        \label{fig:libraryWithBarrel}
         \end{subfigure}
    ~
	\begin{subfigure}[b]{0.14 \textwidth}
        \caption{Ring toy}
        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure3/Figure3_d.png}
        \label{fig:libraryWithRingToy}
    \end{subfigure}
        ~
    	\begin{subfigure}[b]{0.14 \textwidth}
        \caption{Bottle}
        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure3/Figure3_e.png}
        \label{fig:libraryWithChampagneBottle}
    \end{subfigure}
\caption{{\bf Library base scene with inserted objects.} The rendering package can be used to insert objects into base scenes. Each image shows a different object inserted into the Library base scene. The rendering viewpoint was set so that the object was at the center of the images. The full rendered images have been cropped so that the inserted objects are easily visible.}\label{fig:libraryWithTarget}
\end{figure}

@@

In Condition 1, the relative reflectance spectrum of the target object was the only source of scene variation other than the target object LRF.
The reflectance spectra of the background objects and the spectral power distribution of the light sources were held fixed.
In Condition 2, the spectral power distribution of the light sources varied in addition to the relative reflectance spectrum of the target object.
Finally, in Condition 3 three distinct scene factors--target object relative reflectance spectrum, spectral power distribution of the light sources, and reflectance spectra of the background objects
--varied in addition to the target object LRF.
The datasets for Conditions 1 and 2 consisted of 1000 scenes and images, 100 for each of 10 target object LRF values. 
The dataset for Condition 3 consisted of 3000 scenes and images, 300 each for the 10 target LRF values.
The LRF values were equally spaced between 0.2 and 0.6.
More than 90\% of the surface reflectance spectra (generated as described below) fell within this range.
For each LRF value, we generated a different relative target object surface reflectance for each scene. 
% Figure 4
\begin{figure}
	\begin{subfigure}{0.18 \textwidth}
    \centering
        \caption{Target position}
        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure4/Figure4_a.pdf}
        \label{fig:targetPositionVariation}
    \end{subfigure}
    ~
	\begin{subfigure}{0.18 \textwidth}
    \centering
        \caption{Target size/pose}
        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure4/Figure4_b.pdf}
        \label{fig:targetSizeOrientation}
    \end{subfigure}
~
\centering
	\begin{subfigure}{0.18 \textwidth}
    \centering
        \caption{Target spectra}
        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure4/Figure4_c.pdf}
        \label{fig:targetVariation}
    \end{subfigure}
    ~
    \begin{subfigure}{0.18 \textwidth}
    \centering
        \caption{Illumination spectra}
        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure4/Figure4_d.pdf}
        \label{fig:illuminationVariation}
    \end{subfigure}
          ~  
    \begin{subfigure}{0.18 \textwidth}
    \centering
        \caption{Background spectra}
        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure4/Figure4_e.pdf}
        \label{fig:backGroundVariation}
    \end{subfigure}

    \caption{{\bf Scene transformations.} The properties of a visual scene can be broadly classified into two groups: geometrical (a-b) and spectral (c-e). Our rendering package provides control over these properties as illustrated by the columns of the figure. (a) Variation in inserted object positions. (b) Variation in object size and pose. (c) Variation in the surface reflectance of the target object. (d) Variation in the spectral power distributions of the light sources. (e) Variation in surface reflectance of the background objects. All images in this figure are rendered with common scaling and tone mapping.
\label{fig:VWCCTransformations}}
\end{figure}

We used the Library base scene and a spherical target object.
The Library base scene contains 2 area lights. 
We inserted one additional spherical light source into the scene.
In Conditions 2 and 3, the overall intensities of the three light source illumination spectra were equal, while their relative shape varied. 
The overall intensity varied from scene to scene.
The position and size of the inserted object, the inserted light source, and the viewpoint on the scene were held fixed across all 
scenes. The geometry is shown in Figure~\ref{fig:3DScene} below.
Surface and illuminant spectra were sampled according to statistical models of naturally occurring spectra.
Multispectral images ($320 \times 240$ pixels) were rendered at 31 evenly-spaced wavelengths between $400$nm and $700$nm.

% Figure 5: Conditions Studied
\begin{figure}
\centering
	\begin{subfigure}{0.33 \textwidth}
		\caption{Condition 1}
%		\includegraphics[width=\textwidth]{../FiguresDraft5/Figure2/Figure2_a.png}
		\includegraphics[width=\textwidth]{../FiguresDraft5/Figure1/Figure1_b.pdf}
 		\label{fig:backgroundVarying}
	\end{subfigure}
	\begin{subfigure}{0.33 \textwidth}
        \caption{Condition 2}	
        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure5/Figure5_b.pdf}
        \label{fig:targetIlluminantVarying}
    \end{subfigure}
	\begin{subfigure}{0.33 \textwidth}
	\caption{Condition 3}	
        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure5/Figure5_c.pdf}        
        \label{fig:allSpectraVarying}
    \end{subfigure}    
    \caption{{\bf Conditions 1-3:} Illustrative images for the three types of spectral variations studied in this paper. (a) Condition 1: variable target object relative reflectance spectrum, fixed light source spectra, fixed background object spectra (same as Fig.~\ref{fig:introExampleFigure}). 
(b) Condition 2: variable target object relative reflectance spectrum, variable light source spectra, fixed background object spectra. (c) Condition 3: variable target object relative reflectance spectrum, variable light source spectra, variable background object spectra. The spheres in each row of each panel have the same LRF, while the spheres in each column of each panel have the same relative surface reflectance spectrum.  Across panels a-c, spheres in corresponding locations have the same surface reflectance. In all three panels, the overall light source spectra scale factors (see \nameref{Methods}) were drawn from a uniform distribution on the range [0.5, 1.5]. This is smaller than the variation we studied, but allows us to show the variation within the dynamic range available for display in publication. All images in this figure are rendered with common scaling and tone mapping.} 
\label{fig:studiedCases}
\end{figure}

@@

% Figure 6
\begin{figure}
\centering
    \begin{subfigure}[b]{0.24 \textwidth}
    \centering
	\caption{Granada dataset}
        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure6/Figure6_a.pdf}
        \label{fig:granadaData}
    \end{subfigure}
	\begin{subfigure}[b]{0.24 \textwidth}
    \centering
        \caption{Statistical model}
        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure6/Figure6_b.pdf}
        \label{fig:illuminantSamples}
    \end{subfigure}
      	\begin{subfigure}[b]{0.24 \textwidth}
    \centering
        \caption{CIE xy chromaticity}
        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure6/Figure6_c.pdf}
        \label{fig:xyDiagram}
        \end{subfigure}
      	\begin{subfigure}[b]{0.24 \textwidth}
    \centering
        \caption{Color swatches}
        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure6/Figure6_d.pdf}
        \label{fig:sRGBIlluminant}
    \end{subfigure}
    \caption{{\bf Statistical model of illumination spectra:} (a) Normalized Granada dataset. Each spectrum is normalized by its mean power. (b) Sample spectra generated using the statistical model derived from normalized Granada dataset. (c) CIE xy chromaticities of the Granda dataset (black) and the samples shown in panel b (red). (d) sRGB renditions of the samples shown in panel b.}
\label{fig:illuminant}
\end{figure}

Our statistical model approximates normalized spectra from the Granada dataset using the first 6 principle components of the normalized measurements from that dataset.
The distribution of weights on these components is approximated with a 6-dimensional Gaussian, where the mean and covariance matrix match the sample mean and covariance of the weights \cite{BrainardFreeman}. 
To generate a random relative illuminant spectrum, we sample weights randomly from this Gaussian and then perform a weighted sum of the components.
Figure~\ref{fig:illuminantSamples} illustrates the relative spectra of draws obtained using this procedure.
Chromaticities and rendered color renditions of these draws are shown in Figures~\ref{fig:xyDiagram} and ~\ref{fig:sRGBIlluminant}.
Details of the statistical model for illumination are provided in the appendix.

@@

\subsubsection{Surface reflectance spectra}
% Figure 7 Surface Reflectance Data and Model
\begin{figure}
\centering
	\begin{subfigure}{0.24 \textwidth}
    \centering
            \caption{Munsell and Vrhel dataset}
        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure7/Figure7_a.pdf}
        \label{fig:reflectanceSpectra}
    \end{subfigure}
    \begin{subfigure}{0.24 \textwidth}
    \centering
        \caption{Statistical model}
        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure7/Figure7_b.pdf}
        \label{fig:reflectanceSamples}
    \end{subfigure}
    \begin{subfigure}{0.24 \textwidth}
    \centering
    \caption{CIE xy chromaticity}
        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure7/Figure7_c.pdf}
        \label{fig:xyChroReflectance}
    \end{subfigure}    
    \centering
	\begin{subfigure}{0.24 \textwidth}
    \centering
        \caption{Color swatches}
        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure7/Figure7_d.pdf}
        \label{fig:backgroundSwatches}
    \end{subfigure}
    \caption{{\bf Statistical model of surface reflectance:} (a) Surface reflectance spectra from the Munsell and Vrhel datasets. (b) Sample spectra generated using the surface reflectance statistical model. (c) CIE xy chromaticity diagram of the Munsell and Vrhel reflectances (black) and the sample spectra shown in panel b (red). (d) sRGB renditions of the samples shown in panel b, rendered under the CIE D65 daylight spectrum.}
\label{fig:surfaceReflectanceGeneration}
\end{figure}

To generate random reflectance spectra, we employed principles similar to those used to generate random illuminant spectral power distributions.
We used measurements from the Munsell \cite{kelly1943tristimulus} and Vrhel \cite{vrhel1994measurement} surface reflectance datasets to create a dataset containing 632 reflectance spectra (462 from the Munsell data and 170 from the Vrhel data; Figure~\ref{fig:reflectanceSpectra}).
We resampled the spectra to 31 evenly-spaced wavelengths between 400 nm and 700 nm.
Figures~\ref{fig:reflectanceSamples},~\ref{fig:xyChroReflectance}, and~\ref{fig:backgroundSwatches} illustrate reflectance sampled obtained using the model. 
Details of the statistical model for surface reflectance spectra are provided in the appendix.

%Figure 8 Target Surface Reflectance Samples
\begin{figure}
\centering
\includegraphics[width=0.3\textwidth]{../FiguresDraft5/Figure8/Figure8.pdf}
\caption{{\bf Target object surface reflectance spectra:} sRGB renditions of the target object surface reflectance rendered under CIE D65 daylight spectrum. The figure shows 10 random samples at 10 equally spaced LRF levels in the range [0.2, 0.6]. Each row contains 10 random samples of reflectance spectra generated at the LRF shown on the left.}
\label{fig:targetSwatches}
\end{figure}

@@

We focused our analysis on image regions local to the target by cropping the rendered images to $1\degree \times 1\degree$ degrees of visual angle around the target object ($51 \times 51$ pixels; Figure~\ref{fig:croppedImage}).
The local analysis is motivated by the fact that neural receptive fields early in the visual pathways (e.g., retina, primary visual cortex) pool information locally. 
In primary visual cortex, foveal receptive fields have a maximum spatial extent of approximately 1 degree of visual angle \cite{gattass1981visual, gattass1988visuotopic}. 
We sought to understand how well responses from AMA-learned receptive fields at a similar scale could be used to achieve luminance constancy.

>>>>

% \usepackage{lineno}
% \linenumbers
\begin{document}

@@

\section{Introduction}
The perceived color of an object has important behavioral implications because color helps to identify objects and their surface properties \cite{Mollon89, Jacobs81}.
The computational challenge underlying object color perception is that the light reflected from an object depends not just on the object's surface reflectance, but also 
on object-extrinsic factors such as the scene illumination, the pose of the object, and the viewpoint of the observer in the scene (Fig.~\ref{fig:introFigure}a).
To compute a perceptual representation of object color that is correlated with the object's physical surface reflectance, the visual system must account for these object-extrinsic factors.
The ability of a visual system to compute a representation of object color that is stable against variation in object-extrinsic factors is called color constancy. 
A well-studied special case of color constancy is when the stimuli are restricted to be achromatic. 
This special case is called lightness constancy \cite{gilchrist2006seeing}. 
Although human lightness and color constancy are not perfect, they are often very good \cite{FosterColorConstancy, BrainardColorConstancy,adelson2000,kingdom2011lightness}.

@@

% Figure 1: Introduction
\begin{figure}
\centering
%\begin{subfigure}{0.4 \textwidth}
%	\centering
%	\caption{}
%        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure1/Figure1_a.png}
%        \label{fig:introSchematic}
%    \end{subfigure}
%    \begin{subfigure}{0.55 \textwidth}   
%        \caption{}    
%        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure1/Figure1_b.pdf}
%        \label{fig:introExampleFigure}
%    \end{subfigure}
\includegraphics[width=\textwidth]{Figure1.eps}    
    \caption{{\bf Color and luminance constancy:} (a)  The light reflected from an object to the eye depends both on the surface reflectance of the object and on the scene illumination. 
The reflected light also depends on geometric factors, such as the object's shape, pose, and position. 
The human visual system accounts for variations in reflected light due to object-extrinsic factors and produces a percept of object color that is relatively stable across such variations. 
(b) Images of a sphere under a fixed illuminant.  
Down each column, the sphere's luminous reflectance factor (LRF) varies, but its relative reflectance spectrum (i.e. its spectral shape) is held fixed.
Across each row, the relative reflectance spectrum varies, but the LRF is held fixed.
We cast the problem of computational luminance constancy to be that of estimating the LRF of a target object from the image, across variation in other scene factors. 
Specifically, we study variation in target object relative surface reflectance, variation in illumination spectrum, and variation in the surface reflectance of the other objects in the scene.}
\label{fig:introFigure}
 \end{figure}

@@

In this paper, we use high-quality computer graphics to generate large datasets of naturalistic images where the surface reflectance corresponding to each image pixel is known. 
This approach allows us to investigate computational color constancy with naturalistic stimuli, while retaining the ability to control the properties of objects and illuminants. We tackle the specific problem of luminance constancy, a constitutive component of the more general color constancy problem (Fig.~\ref{fig:introFigure}b).

@@

\section*{Methods} \label{Methods}
% Figure 2
\begin{figure}
\centering
%\begin{subfigure}[b]{0.22 \textwidth}
%        \caption{Library }
%        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure2/Figure2_a.pdf}
%        \label{fig:baseSceneLibrary}
%    \end{subfigure}
%    ~
%    \begin{subfigure}[b]{0.22 \textwidth}
%        \caption{Mill}    
%        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure2/Figure2_b.pdf}
%        \label{fig:baseSceneMill}
%    \end{subfigure}    
%    ~
%    \begin{subfigure}[b]{0.22 \textwidth}
%        \caption{Table-Chairs}    
%        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure2/Figure2_c.pdf}
%        \label{fig:baseSceneTableChairs}
%    \end{subfigure}
\includegraphics[width=\textwidth]{Figure2.eps}
    \caption{{\bf Base scenes.} Each image shows a rendering of one base scene without additional inserted objects.  The reflectance spectra of the distinct surfaces and the spectral power distributions of the light sources in each scene have been assigned randomly from statistical models of naturally occurring spectra. The images have been scaled and tone mapped individually for illustrative purposes.}
\label{fig:baseScenes}
\end{figure}

@@

% Figure 3
\begin{figure}
\centering
%    \begin{subfigure}[b]{0.14 \textwidth}
%        \caption{Big-ball}
%        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure3/Figure3_a.png}
%        \label{fig:libraryWithBigBall}
%    \end{subfigure}
%     ~ 
%    \begin{subfigure}[b]{0.14 \textwidth}
%        \caption{Xylophone}
%        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure3/Figure3_b.png}
%        \label{fig:libraryWithXylophone}
%    \end{subfigure}
%     ~ 
%    \begin{subfigure}[b]{0.14 \textwidth}
%        \caption{Barrel}
%        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure3/Figure3_c.png}
%        \label{fig:libraryWithBarrel}
%         \end{subfigure}
%    ~
%	\begin{subfigure}[b]{0.14 \textwidth}
%        \caption{Ring toy}
%        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure3/Figure3_d.png}
%        \label{fig:libraryWithRingToy}
%    \end{subfigure}
%        ~
%    	\begin{subfigure}[b]{0.14 \textwidth}
%        \caption{Bottle}
%        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure3/Figure3_e.png}
%        \label{fig:libraryWithChampagneBottle}
%    \end{subfigure}
\includegraphics[width=\textwidth]{Figure3.eps}
\caption{{\bf Library base scene with inserted objects.} The rendering package can be used to insert objects into base scenes. Each image shows a different object inserted into the Library base scene. The rendering viewpoint was set so that the object was at the center of the images. The full rendered images have been cropped so that the inserted objects are easily visible.}\label{fig:libraryWithTarget}
\end{figure}

@@

In Condition 1, the relative reflectance spectrum of the target object was the only source of scene variation other than the target object LRF.
The reflectance spectra of the background objects and the spectral power distribution of the light sources were held fixed.
In Condition 2, the spectral power distribution of the light sources varied in addition to the relative reflectance spectrum of the target object.
Finally, in Condition 3 three distinct scene factors--target object relative reflectance spectrum, spectral power distribution of the light sources, and reflectance spectra of the background objects
--varied in addition to the target object LRF.
The datasets for Conditions 1 and 2 consisted of 1000 scenes and images, 100 for each of 10 target object LRF values. 
The dataset for Condition 3 consisted of 3000 scenes and images, 300 each for the 10 target LRF values.
The LRF values were equally spaced between 0.2 and 0.6.
More than 90\% of the surface reflectance spectra (generated as described below) fell within this range.
For each LRF value, we generated a different relative target object surface reflectance for each scene. 
% Figure 4
\begin{figure}
%	\begin{subfigure}{0.18 \textwidth}
%    \centering
%        \caption{Target position}
%        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure4/Figure4_a.pdf}
%        \label{fig:targetPositionVariation}
%    \end{subfigure}
%    ~
%	\begin{subfigure}{0.18 \textwidth}
%    \centering
%        \caption{Target size/pose}
%        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure4/Figure4_b.pdf}
%        \label{fig:targetSizeOrientation}
%    \end{subfigure}
%~
%\centering
%	\begin{subfigure}{0.18 \textwidth}
%    \centering
%        \caption{Target spectra}
%        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure4/Figure4_c.pdf}
%        \label{fig:targetVariation}
%    \end{subfigure}
%    ~
%    \begin{subfigure}{0.18 \textwidth}
%    \centering
%        \caption{Illumination spectra}
%        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure4/Figure4_d.pdf}
%        \label{fig:illuminationVariation}
%    \end{subfigure}
%          ~  
%    \begin{subfigure}{0.18 \textwidth}
%    \centering
%        \caption{Background spectra}
%        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure4/Figure4_e.pdf}
%        \label{fig:backGroundVariation}
%    \end{subfigure}
\includegraphics[width=\textwidth]{Figure4.eps}
    \caption{{\bf Scene transformations.} The properties of a visual scene can be broadly classified into two groups: geometrical (a-b) and spectral (c-e). Our rendering package provides control over these properties as illustrated by the columns of the figure. (a) Variation in inserted object positions. (b) Variation in object size and pose. (c) Variation in the surface reflectance of the target object. (d) Variation in the spectral power distributions of the light sources. (e) Variation in surface reflectance of the background objects. All images in this figure are rendered with common scaling and tone mapping.
\label{fig:VWCCTransformations}}
\end{figure}

We used the Library base scene and a spherical target object.
The Library base scene contains 2 area lights. 
We inserted one additional spherical light source into the scene.
In Conditions 2 and 3, the overall intensities of the three light source illumination spectra were equal, while their relative shape varied. 
The overall intensity varied from scene to scene.
The position and size of the inserted object, the inserted light source, and the viewpoint on the scene were held fixed across all 
scenes. The geometry is shown in Figure~\ref{fig:figure9}a below.
Surface and illuminant spectra were sampled according to statistical models of naturally occurring spectra.
Multispectral images ($320 \times 240$ pixels) were rendered at 31 evenly-spaced wavelengths between $400$nm and $700$nm.

% Figure 5: Conditions Studied
\begin{figure}
\centering
%	\begin{subfigure}{0.33 \textwidth}
%		\caption{Condition 1}
%%		\includegraphics[width=\textwidth]{../FiguresDraft5/Figure2/Figure2_a.png}
%		\includegraphics[width=\textwidth]{../FiguresDraft5/Figure1/Figure1_b.pdf}
% 		\label{fig:backgroundVarying}
%	\end{subfigure}
%	\begin{subfigure}{0.33 \textwidth}
%        \caption{Condition 2}	
%        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure5/Figure5_b.pdf}
%        \label{fig:targetIlluminantVarying}
%    \end{subfigure}
%	\begin{subfigure}{0.33 \textwidth}
%	\caption{Condition 3}	
%        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure5/Figure5_c.pdf}        
%        \label{fig:allSpectraVarying}
%    \end{subfigure}    
\includegraphics[width=\textwidth]{Figure5.eps}        
    \caption{{\bf Conditions 1-3:} Illustrative images for the three types of spectral variations studied in this paper. (a) Condition 1: variable target object relative reflectance spectrum, fixed light source spectra, fixed background object spectra (same as Fig.~\ref{fig:introFigure}b). 
(b) Condition 2: variable target object relative reflectance spectrum, variable light source spectra, fixed background object spectra. (c) Condition 3: variable target object relative reflectance spectrum, variable light source spectra, variable background object spectra. The spheres in each row of each panel have the same LRF, while the spheres in each column of each panel have the same relative surface reflectance spectrum.  Across panels a-c, spheres in corresponding locations have the same surface reflectance. In all three panels, the overall light source spectra scale factors (see \nameref{Methods}) were drawn from a uniform distribution on the range [0.5, 1.5]. This is smaller than the variation we studied, but allows us to show the variation within the dynamic range available for display in publication. All images in this figure are rendered with common scaling and tone mapping.} 
\label{fig:studiedCases}
\end{figure}

@@

% Figure 6
\begin{figure}
\centering
%    \begin{subfigure}[b]{0.24 \textwidth}
%    \centering
%	\caption{Granada dataset}
%        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure6/Figure6_a.pdf}
%        \label{fig:granadaData}
%    \end{subfigure}
%	\begin{subfigure}[b]{0.24 \textwidth}
%    \centering
%        \caption{Statistical model}
%        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure6/Figure6_b.pdf}
%        \label{fig:illuminantSamples}
%    \end{subfigure}
%      	\begin{subfigure}[b]{0.24 \textwidth}
%    \centering
%        \caption{CIE xy chromaticity}
%        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure6/Figure6_c.pdf}
%        \label{fig:xyDiagram}
%        \end{subfigure}
%      	\begin{subfigure}[b]{0.24 \textwidth}
%    \centering
%        \caption{Color swatches}
%        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure6/Figure6_d.pdf}
%        \label{fig:sRGBIlluminant}
%    \end{subfigure}
\includegraphics[width=\textwidth]{Figure6.eps}
    \caption{{\bf Statistical model of illumination spectra:} (a) Normalized Granada dataset. Each spectrum is normalized by its mean power. (b) Sample spectra generated using the statistical model derived from normalized Granada dataset. (c) CIE xy chromaticities of the Granda dataset (black) and the samples shown in panel b (red). (d) sRGB renditions of the samples shown in panel b.}
\label{fig:illuminant}
\end{figure}

Our statistical model approximates normalized spectra from the Granada dataset using the first 6 principle components of the normalized measurements from that dataset.
The distribution of weights on these components is approximated with a 6-dimensional Gaussian, where the mean and covariance matrix match the sample mean and covariance of the weights \cite{BrainardFreeman}. 
To generate a random relative illuminant spectrum, we sample weights randomly from this Gaussian and then perform a weighted sum of the components.
Figure~\ref{fig:illuminant}b illustrates the relative spectra of draws obtained using this procedure.
Chromaticities and rendered color renditions of these draws are shown in Figures~\ref{fig:illuminant}c and ~\ref{fig:illuminant}d.
Details of the statistical model for illumination are provided in the appendix.

@@

\subsubsection{Surface reflectance spectra}
% Figure 7 Surface Reflectance Data and Model
\begin{figure}
\centering
%	\begin{subfigure}{0.24 \textwidth}
%    \centering
%            \caption{Munsell and Vrhel dataset}
%        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure7/Figure7_a.pdf}
%        \label{fig:reflectanceSpectra}
%    \end{subfigure}
%    \begin{subfigure}{0.24 \textwidth}
%    \centering
%        \caption{Statistical model}
%        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure7/Figure7_b.pdf}
%        \label{fig:reflectanceSamples}
%    \end{subfigure}
%    \begin{subfigure}{0.24 \textwidth}
%    \centering
%    \caption{CIE xy chromaticity}
%        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure7/Figure7_c.pdf}
%        \label{fig:xyChroReflectance}
%    \end{subfigure}    
%    \centering
%	\begin{subfigure}{0.24 \textwidth}
%    \centering
%        \caption{Color swatches}
%        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure7/Figure7_d.pdf}
%        \label{fig:backgroundSwatches}
%    \end{subfigure}
    \includegraphics[width=\textwidth]{Figure7.eps}
    \caption{{\bf Statistical model of surface reflectance:} (a) Surface reflectance spectra from the Munsell and Vrhel datasets. (b) Sample spectra generated using the surface reflectance statistical model. (c) CIE xy chromaticity diagram of the Munsell and Vrhel reflectances (black) and the sample spectra shown in panel b (red). (d) sRGB renditions of the samples shown in panel b, rendered under the CIE D65 daylight spectrum.}
\label{fig:surfaceReflectanceGeneration}
\end{figure}

To generate random reflectance spectra, we employed principles similar to those used to generate random illuminant spectral power distributions.
We used measurements from the Munsell \cite{kelly1943tristimulus} and Vrhel \cite{vrhel1994measurement} surface reflectance datasets to create a dataset containing 632 reflectance spectra (462 from the Munsell data and 170 from the Vrhel data; Figure~\ref{fig:surfaceReflectanceGeneration}a).
We resampled the spectra to 31 evenly-spaced wavelengths between 400 nm and 700 nm.
Figures~\ref{fig:surfaceReflectanceGeneration}b,~\ref{fig:surfaceReflectanceGeneration}c, and~\ref{fig:surfaceReflectanceGeneration}d illustrate reflectance sampled obtained using the model. 
Details of the statistical model for surface reflectance spectra are provided in the appendix.

%Figure 8 Target Surface Reflectance Samples
\begin{figure}
\centering
\includegraphics[width=0.3\textwidth]{Figure8.eps}
\caption{{\bf Target object surface reflectance spectra:} sRGB renditions of the target object surface reflectance rendered under CIE D65 daylight spectrum. The figure shows 10 random samples at 10 equally spaced LRF levels in the range [0.2, 0.6]. Each row contains 10 random samples of reflectance spectra generated at the LRF shown on the left.}
\label{fig:targetSwatches}
\end{figure}

@@

We focused our analysis on image regions local to the target by cropping the rendered images to $1\degree \times 1\degree$ degrees of visual angle around the target object ($51 \times 51$ pixels; Figure~\ref{fig:figure9}b).
The local analysis is motivated by the fact that neural receptive fields early in the visual pathways (e.g., retina, primary visual cortex) pool information locally. 
In primary visual cortex, foveal receptive fields have a maximum spatial extent of approximately 1 degree of visual angle \cite{gattass1981visual, gattass1988visuotopic}. 
We sought to understand how well responses from AMA-learned receptive fields at a similar scale could be used to achieve luminance constancy.

We modeled a visual system having typical optical blurring (including axial chromatic aberration, \citeNP{marimont1994matching}), and typical spatial sampling with an interleaved rectangular mosaic of long (L), middle (M)  and short (S) wavelength-sensitive cones (\citeNP{brainard2015color}; Fig.~\ref{fig:figure9}c). 
The cone mosaic contained L:M:S cones in approximately the ratio 0.6:0.3:0.1 (1523 L cones, 801 M cones, 277 S cones) and with spectral sensitivities derived from the CIE physiological standard \cite{CIE86}.
Cone excitations were taken as the number of photopigment isomerizations, assuming an integration time of 100 msec. 
The Poisson nature of the photopigment isomerization was also included \cite{hecht1942energy}. 
This modeling was implemented using the software infrastructure provided by ISETBio (\href{https://isetbio.org}{https://isetbio.org}).
